\TheTitle

### 2019-11-22 Paper1/one_shot_ipm.tex
local convergence comment

In the following, we will show that this iteration converges, if the chosen initial condition is sufficiently close to the steady state solution. For this we take an approach commonly chosen to prove local convergence properties of Newton's method: In Theorem \ref{th:Contractive}, we show that the iteration function is contractive at its fixed point and conclude in Theorem \ref{th:localConvergence} that this yields local convergence: \frama{Nico meinte wir sollten hier in die Voraussetzung packen, dass wir nah genug an der richtigen Loesung sind (Einzugsbereich des Newton) um das Wort 'local' zu vermeiden. Manchmal stören sich die Reviewer daran.}

>>>>

In the following, we will show that this iteration converges, if the chosen initial condition is sufficiently close to the steady state solution. For this we take an approach commonly chosen to prove local convergence properties of Newton's method: In Theorem \ref{th:Contractive}, we show that the iteration function is contractive at its fixed point and conclude in Theorem \ref{th:localConvergence} that this yields local convergence. Hence, we preserve the convergence results of the original IPM method, which uses Newton's method, i.e. converges locally as well.
